\title{Fontaine-Wintenberger Theorem}


% \home{https://lean4fonwinteam.github.io/FontaineWintenberger/}
%\home{localhost:8080}
\input{homeurl}
\github{https://github.com/Lean4FonWinTeam/FontaineWintenberger/}
%\dochome{https://lean4fonwinteam.github.io/FontaineWintenberger/doc/}
%\dochome{localhost:8080/doc}

\maketitle


\tableofcontents

The first section records currently missing infrastructures in Mathlib. The following three sections serves for the tilting equivalence. The remaining parts serves for the concrete example of cyclotomic fields.

\section{Missing Infrastructures in Mathlib}
In this section, we record the missing infrastructures in a rough way. All definitions and theorem under a same topic will be bundled in a single definition.

\begin{definition}
    \label{Relate Galois Group with Category of Finite Field Extensions}
    \notready

    Inteperate Galois group as functors on $ \text{FinExt}_K $ satisfying certain property. Show that $\text{FinExt}_K \simeq \text{FinExt}_K'$ induces an isomorphism $\Gal_K \simeq \Gal_{K'}$.
\end{definition}

\section{Perfectoid Fields}

\begin{definition}[Perfectoid Fields]
    \label{Perfectoid Field}
    \lean{PerfectoidField}
    % \uses{Valuation.integer}

    Let $K$ be a topological field. We say that $K$ is a \emph{perfectoid field} if and only if the following conditions are satisfied:\\
    (a) the topology on K is induced by a valuation $\| \cdot \| : K \to \R_{\ge0}$, and $K$ is complete for this topology;\\
    (b) there exists a non-unit $\pi \in \O_K$ such that $p \in \pi^p \O_K$;\\
    (c) every element of $\O_K/p\O_K$ is a $p$th-power.
\end{definition}



\section{Almost Mathematics}

\section{The Tilting Equivalence for Perfectoid Fields}

\begin{definition}
    \label{Tilting Functor (Finite Extension)}
    \notready

    There is a functor 
    \begin{align*}
        \left \{ \text{finite field extensions of } K \right \} & \to \left \{ \text{finite fields extension of} K^\flat \right \} \\
        L & \mapsto L^\flat
    \end{align*}

\end{definition}

\begin{theorem}
    \label{tilting_finite_degree_preserving}
    \uses{Tilting Functor (Finite Extension)}
    \notready

    The functor above is degree preserving.
\end{theorem}

\begin{proof}
    \notready

    sorry
\end{proof}

\begin{theorem}
    \label{tilting_finite_equivalence_of_category}
    \uses{Tilting Functor (Finite Extension)}
    \notready

    The functor above is an equivalence of category.
\end{theorem}

\begin{proof}
    \uses{tilting_finite_degree_preserving}
    \notready

    sorry
\end{proof}

\begin{definition}[Galois Isomorphism of Perfectoid Fields]
    \label{Galois Isomorphism of Perfectoid Fields}

    \uses{
        Tilting Functor (Finite Extension), 
        tilting_finite_equivalence_of_category, 
        Relate Galois Group with Category of Finite Field Extensions
        }
    \notready

    There exists an isomorphism of absolute Galois groups
    $$ \Gal_K \simeq \Gal_{K^\flat}.$$
\end{definition}

\section{Calculation of $\Q_p^{\cyc}$}


\section{Example}
Here you can use LaTex. \cite{marcus}. You must cite something to make it work.

\input{demo}
